Is malaria control profitable? Return on investment of privately-managed residential fumigations at a large sugarcane processing facility in Southern Mozambique

### 2018-05-06 inst/rmd/paper.tex
externalities text

We sought to understand the effect of IRS on individual workers'
likelihood of absence from work as well as their likelihood of clinical
malaria. To estimate this effect, we estimated separate models for
absence and illness. We employed linear mixed effects models (Minalu et
al., 2011) (Liu et al., 2010) (with individual worker fixed effects, and
random effects for other covariates) in lieu of interrupted time series
(Lopez Bernal et al., 2016) so as to explicitly adjust for confounders
(Bell and Jones, 2014). We divide into 4 different models for different
worker types, so as to account for the potential time-varying effects of
worker type on risk of malaria. Our model specification is as follows

\[
\hat{Y_{it}} = \hat{\beta}_{0} +  \hat{\beta}_{1}\text{Season}_{t} * (\hat{\beta}_2{IRS_{it}}*\hat{\beta}_3{IRStime_{it}}) + \alpha_i + \delta_t + \upsilon_{it}
\]

\(\hat{Y}_{it}\) is the rate of absence. \(\beta_{1}\) is the binary
``season'' variable, imputed from overall district clinical incidence.
Our intervention is whether the residence of the worker in question was
treated in the last year, and, if so, the time since treatment,
represented, respectively, by \(\beta_{2}\) and \(\beta_{3}\).
\(\alpha_i\) reprsents the time invariant worker fixed effects, and
\(\delta_i\) represents the fixed effect of the particular malaria
season. \(\upsilon\) is the error term.

@@

Details will go here about externalities (neighborhood effects, positive
spillover to district, negative spillover from district, how large firm
may mean that most positive externalities are absorbed by the firm, and
not many negative externalities, but maybe with a smaller firm it
wouldn't work as well)\todo{NOT DONE YET.}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
Variable &   & Treatment workers & Treatment days & Control workers & Control days \\ 
  \hline
Department & Administrative &  35 & 12523 & 157 & 173151 \\ 
   & Factory &  71 & 20533 & 453 & 280416 \\ 
   & Field & 410 & 91302 & 2691 & 1181175 \\ 
  Sex & F & 228 & 47907 & 1274 & 489484 \\ 
   & M & 288 & 76451 & 2027 & 1145258 \\ 
  Status & Permanent & 127 & 47075 & 500 & 655311 \\ 
   & Temporary & 389 & 77283 & 2801 & 979431 \\ 
  Age & 20 & 140 & 29463 & 960 & 347758 \\ 
   & 30 & 176 & 39119 & 1225 & 550783 \\ 
   & 40 & 123 & 30186 & 652 & 366936 \\ 
   & 50 &  58 & 18881 & 344 & 268877 \\ 
   & 60 &  17 & 5893 & 116 & 96555 \\ 
   & 70 &   2 & 816 &   4 & 3833 \\ 
   \hline
\end{tabular}
\caption{Overall worker characteristics} 
\end{table}

@@

\textbf{Fumigations}: During the period from January 1st, 2013 through
December 31st, 2016, the Maragra Malaria Control Unit carried out 11,007
episodes of fumigation of residential ``agregados'' (household
combinations), for a total of 13,260 building-fumigation combinations.
The total number of unique agregados sprayed during this period was
3,998. Among the 3,362 workers for whom we have reliable absenteeism and
residential data, 692 had their homes fumigated at least once (the
majority of workers live off of the facility).

\textbf{Absences}: We observed 1,759,100 unique worker-days among the
3,362 workers. The all-period average absenteeism rate was 5.56\%,
though this rate varied widely as a function of worker department, sex,
residence, and season (table 1).

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
Variable &  & 2013 & 2014 & 2015 & 2016 \\ 
  \hline
Malaria season & Low & 5.2\% & 7\% & 5.4\% & 3.3\% \\ 
   & High & 8.2\% & 12.8\% & 6.3\% & 2.7\% \\ 
  Worker type & Field worker & 4.4\% & 7.6\% & 3.9\% & 1.7\% \\ 
   & Not field worker & 10.7\% & 12.4\% & 11.5\% & 9.6\% \\ 
  Contract & Permanent & 12.1\% & 12.6\% & 12\% & 10.2\% \\ 
   & Temporary & 0.1\% & 5\% & 2.3\% & 0.5\% \\ 
  Sex & F & 4\% & 8.1\% & 4.4\% & 1.9\% \\ 
   & M & 8.1\% & 10\% & 6.5\% & 3.7\% \\ 
  Residence & Off site & 6.4\% & 9.6\% & 5.9\% & 3\% \\ 
   & On site & 9.4\% & 9.7\% & 6.1\% & 3.1\% \\ 
  Precipitation & Dry & 5.4\% & 7.7\% & 4.8\% & 2.4\% \\ 
   & Rainy & 7.9\% & 10.6\% & 7\% & 3.3\% \\ 
   \hline
\end{tabular}
\caption{Absenteeism rate by year and worker characteristics} 
\end{table}

@@

The model results for all cause absenteeism (table 4) suggest a
significant decrease in absenteeism following the administration of IRS.
The effect is ambivalent among temporary workers, whereas among
permanent workers the administration of IRS decreases absenteeism betwen
2.5 and 8.4 percentage points in the 2-9 month following administration.
These effects are consistent with IRS decreasing absence through the
medium of malaria, since (a) the effect is not as strong in the first
month (potentially during the parasite incubation phase), the effect is
stronger on field workers (who are more socioeconomically the
demographic at greater risk of malaria than their administrative
counterparts), and the effect is ambivalent among temporary workers
(since the protective effect of IRS is only a function of the amount of
time that the worker spends in the fumigated house).

\begin{table}

\caption{\label{tab:unnamed-chunk-28}All cause absenteeism: model results}
\centering
\begin{tabular}[t]{ll}
\toprule
Term & Estimate\\
\midrule
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Malaria season & 2.533 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & 5.382 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & 4.747 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -2.669 (P<0.001)\\
\hspace{1em}Precipitation (mm) & 0.206 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -6.262 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -8.388 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -3.71 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Malaria season & 0.957 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & -0.987 (P=0.071)\\
\hspace{1em}Months since IRS: 02-04 & 4.375 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -0.55 (P=0.254)\\
\hspace{1em}Precipitation (mm) & 0.548 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 1.787 (P=0.016)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -5.208 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -2.04 (P=0.003)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Malaria season & -0.368 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & -0.075 (P=0.526)\\
\hspace{1em}Months since IRS: 02-04 & -0.193 (P=0.072)\\
\hspace{1em}Months since IRS: 05-09 & -0.036 (P=0.738)\\
\hspace{1em}Precipitation (mm) & 0.02 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -0.154 (P=0.406)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 0.297 (P=0.05)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & 0.041 (P=0.769)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Malaria season & 2.025 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & -2.536 (P=0.134)\\
\hspace{1em}Months since IRS: 02-04 & -1.177 (P=0.282)\\
\hspace{1em}Months since IRS: 05-09 & -1.821 (P=0.084)\\
\hspace{1em}Precipitation (mm) & 0.078 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 6.121 (P=0.002)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 1.333 (P=0.343)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -4.639 (P<0.001)\\
\bottomrule
\end{tabular}
\end{table}

The model results for sickness only absenteeism (table 5) suggest that
IRS has a significant effect on permanent field workers. The effect is
directionally similar among temporary fieldworkers (but does not reach
the level of significance). Among non-fieldworkers, the effect of IRS is
mixed.

\begin{table}

\caption{\label{tab:unnamed-chunk-29}Sick absenteeism only: model results}
\centering
\begin{tabular}[t]{ll}
\toprule
Term & Estimate\\
\midrule
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Malaria season & -0.073 (P=0.089)\\
\hspace{1em}Months since IRS: 01 & 0.891 (P<0.001)\\
\hspace{1em}Months since IRS: 02-04 & 1.223 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & -0.236 (P=0.249)\\
\hspace{1em}Precipitation (mm) & 0 (P=0.984)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -1.501 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -0.597 (P=0.031)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -0.484 (P=0.097)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Malaria season & -0.056 (P=0.204)\\
\hspace{1em}Months since IRS: 01 & -0.667 (P=0.003)\\
\hspace{1em}Months since IRS: 02-04 & 0.904 (P<0.001)\\
\hspace{1em}Months since IRS: 05-09 & 0.127 (P=0.526)\\
\hspace{1em}Precipitation (mm) & -0.002 (P=0.565)\\
\hspace{1em}Malaria season:Months since IRS: 01 & 1.121 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -0.122 (P=0.652)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & 1.198 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Malaria season & -0.106 (P<0.001)\\
\hspace{1em}Months since IRS: 01 & 0.029 (P=0.545)\\
\hspace{1em}Months since IRS: 02-04 & 0.04 (P=0.35)\\
\hspace{1em}Months since IRS: 05-09 & -0.046 (P=0.291)\\
\hspace{1em}Precipitation (mm) & 0 (P=0.966)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -0.108 (P=0.148)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & -0.032 (P=0.595)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & -0.052 (P=0.36)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Malaria season & -0.135 (P=0.236)\\
\hspace{1em}Months since IRS: 01 & 1.427 (P=0.092)\\
\hspace{1em}Months since IRS: 02-04 & -0.569 (P=0.299)\\
\hspace{1em}Months since IRS: 05-09 & -1.42 (P=0.007)\\
\hspace{1em}Precipitation (mm) & -0.005 (P=0.613)\\
\hspace{1em}Malaria season:Months since IRS: 01 & -1.796 (P=0.069)\\
\hspace{1em}Malaria season:Months since IRS: 02-04 & 2.479 (P<0.001)\\
\hspace{1em}Malaria season:Months since IRS: 05-09 & 0.18 (P=0.794)\\
\bottomrule
\end{tabular}
\end{table}

This section is in progress. Looking at neighborhood effects,
core-periphery effects, etc.

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-33-1.pdf}
\caption{i. Absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-34-1.pdf}
\caption{i. Sick absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}

@@

@@

@@

@@

\hypertarget{ref-Lopez_Bernal_2016}{}
Lopez Bernal, J., Cummins, S., Gasparrini, A., 2016. Interrupted time
series regression for the evaluation of public health interventions: A
tutorial. International Journal of Epidemiology dyw098.
\url{https://doi.org/10.1093/ije/dyw098}

>>>>

We sought to understand the effect of IRS on individual workers'
likelihood of absence from work as well as their likelihood of clinical
malaria. To estimate this effect, we estimated separate models for
absence and illness. We employed linear mixed effects models (Minalu et
al., 2011) (Liu et al., 2010) (with individual worker fixed effects, and
random effects for other covariates) so as to explicitly adjust for
confounders (Bell and Jones, 2014). We divide into 4 different models
for different worker types, so as to account for the potential
time-varying effects of worker type on risk of malaria.

The administration of insecticide at a worker's residence (indoor
residual spraying or IRS) likely protects that worker from malaria
infection by killing the vectors (mosquitoes) that land on the
building's walls. However, it is also highly likely that the protective
effective of IRS ``spills over'' to others who live nearby. This
positive spillover effect would theoretically go through two channels:
(i) via a reduction of mosquitoes in the vicinity and (ii) via a
reduction of the malaria parasite in the blood of humans in the vicinity
(ie, the parasite ``reservoir''). This document describes our method for
assessing the existence and magnitude of positive spillover of IRS in
the Maragra workers' data. We devise a time-specific household
``protection'' score based on the theoretical effectiveness of IRS, and
then use that protection score to develop a time-place specific ``herd
protection'' score based on a weighted average of nearby household
protection scores.

We consider a house's ``herd'' protection level (ie, the protection
conferred to the house through externality) to be the average of the
other houses' non-herd protection levels, weighted by the distance to
the house in question. The below is an illustration of a house (the red
x) and the neighboring houses (circles). The ``weight'' of each house is
indicated by the circle size, and the protection level of the house is
indicated by the shading of the circle.

However, this consideration misses one important dimension: density. The
below house's weighted average protection score is identical to that of
the above house. In other words, at the time in question, at both
locations, the percentage of houses with IRS coverage is the same, and
the (weighted) average time since IRS is the same. However, the below
house is likely much more protected than the above, given the
\emph{absolute} number of nearby IRS-protected houses.

Our approach is this: rather than using a weighted average of each
household's individual protection score, we instead use a weighted sum.
A particular household's herd protection score at any given time is the
sum of all households' individual protection scores at that time
multiplied by those households' distance weights.

The summation of (a) the IRS level of other houses at a certain time,
(b) weighted by the distance of those houses to the house in question,
(c) limited to only the 1 km radius multiplied yields a ``herd
protection score''.

This score is conceptually similar to Cohen and Dupas' quantification of
the positive externalities of ITN (bednet) use in Kenya (Cohen and
Dupas, 2010) in that it attempts to estimate the protection conferred to
``non-users'' by users and uses a ``weighted sum'' (as opposed to
average). Our approach differs in that the time dimension for IRS is
much more important than ITN (ie, IRS is not a binary but rather a
waning function, as described previously), requiring us to create herd
scores for every day.

Our approach can be justified in that previous studies have found strong
positive health externalities in malaria interventions related to ITN
coverage (Alaii et al., 2003). No studies exist on positive
externalities for IRS coverage, but to the extent that the mechanisms
for the reduction in infection are similar (reduction in the natural
reservoir of the disease, reduction in the number of vectors, etc.), it
is reasonable to assume similar effects. Additionally, we using weighted
distance for our score calculation (rather than simply defining a radius
threshold) because of previous studies' findings that there is a linear
decline in protection conferred to others with greater distance from an
intervention (Binka et al., 2007)

\subsubsection{Econometric model}\label{econometric-model}

Our model specification is as follows

\[
\hat{Y_{it}} = \hat{\beta}_{0} +  \hat{\beta}_{1}\text{Season}_{t} * (\hat{\beta}_2{IRS_{it}}*\hat{\beta}_3{IRStime_{it}}) +  \hat{\beta}_4{Herd_{it}} +  \alpha_i + \delta_t + \upsilon_{it}
\]

\(\hat{Y}_{it}\) is the rate of absence. \(\beta_{1}\) is the binary
``season'' variable, imputed from overall district clinical incidence.
Our intervention is whether the residence of the worker in question was
treated in the last year, and, if so, the time since treatment,
represented, respectively, by \(\beta_{2}\) and \(\beta_{3}\).
\(\beta_{4}\) \textbf{represents the distance-weighted herd protection
score}. \(\alpha_i\) represents the time invariant worker fixed effects,
and \(\delta_i\) represents the fixed effect of the particular malaria
season. \(\upsilon\) is the error term.

@@

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
Variable &   & Treatment workers & Treatment days & Control workers & Control days \\ 
  \hline
Department & Administrative &  38 & 47992 &   0 &   0 \\ 
   & Factory & 109 & 78821 &   0 &   0 \\ 
   & Field & 545 & 268206 &   0 &   0 \\ 
  Sex & F & 310 & 139959 &   0 &   0 \\ 
   & M & 382 & 255060 &   0 &   0 \\ 
  Status & Permanent & 128 & 182199 &   0 &   0 \\ 
   & Temporary & 564 & 212820 &   0 &   0 \\ 
  Age & 20 & 200 & 81640 &   0 &   0 \\ 
   & 30 & 242 & 124339 &   0 &   0 \\ 
   & 40 & 154 & 101317 &   0 &   0 \\ 
   & 50 &  68 & 63739 &   0 &   0 \\ 
   & 60 &  26 & 22257 &   0 &   0 \\ 
   & 70 &   2 & 1727 &   0 &   0 \\ 
   \hline
\end{tabular}
\caption{Overall worker characteristics} 
\end{table}

@@

\textbf{Fumigations}: During the period from January 1st, 2013 through
December 31st, 2016, the Maragra Malaria Control Unit carried out 11,007
episodes of fumigation of residential ``agregados'' (household
combinations), for a total of 13,260 building-fumigation combinations.
The total number of unique agregados sprayed during this period was
3,998. Among the 692 workers for whom we have reliable absenteeism and
residential data, 562 had their homes fumigated at least once (the
majority of workers live off of the facility).

\textbf{Absences}: We observed 1,759,100 unique worker-days among the
692 workers. The all-period average absenteeism rate was 5.56\%, though
this rate varied widely as a function of worker department, sex,
residence, and season (table 1).

\begin{table}[ht]
\centering
\begin{tabular}{rlllll}
  \hline
Variable &  & 2013 & 2014 & 2015 & 2016 \\ 
  \hline
Malaria season & Low & 7.5\% & 6.6\% & 5.5\% & 3.4\% \\ 
   & High & 10.7\% & 13.4\% & 6.4\% & 2.7\% \\ 
  Worker type & Field worker & 7.1\% & 8.7\% & 3.9\% & 1.9\% \\ 
   & Not field worker & 11.5\% & 10.8\% & 10.7\% & 8.2\% \\ 
  Contract & Permanent & 12.8\% & 12.5\% & 11.2\% & 9.5\% \\ 
   & Temporary & 0.1\% & 4\% & 2.1\% & 0.5\% \\ 
  Sex & F & 7.1\% & 8.6\% & 4.4\% & 2.3\% \\ 
   & M & 10.4\% & 10\% & 6.9\% & 3.8\% \\ 
  Residence & On site & 9.4\% & 9.7\% & 6.1\% & 3.1\% \\ 
  Precipitation & Dry & 7.4\% & 7.5\% & 4.9\% & 2.4\% \\ 
   & Rainy & 10.5\% & 10.8\% & 7.1\% & 3.4\% \\ 
   \hline
\end{tabular}
\caption{Absenteeism rate by year and worker characteristics} 
\end{table}

@@

The model results for all cause absenteeism (table 4) suggest a
significant decrease in absenteeism following the administration of IRS.
The effect is ambivalent among temporary workers, whereas among
permanent workers the administration of IRS decreases absenteeism by
xxx. These effects are consistent with IRS decreasing absence through
the medium of malaria, since (a) the effect is not as strong in the
first month (potentially during the parasite incubation phase), the
effect is stronger on field workers (who are more socioeconomically the
demographic at greater risk of malaria than their administrative
counterparts), and the effect is ambivalent among temporary workers
(since the protective effect of IRS is only a function of the amount of
time that the worker spends in the fumigated house).

\begin{longtable}[t]{ll}
\caption{\label{tab:unnamed-chunk-27}All absenteeism with herd immunity: model results}\\
\toprule
Term & Estimate\\
\midrule
\endfirsthead
\caption[]{All absenteeism with herd immunity: model results \textit{(continued)}}\\
\toprule
Term & Estimate\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent field worker}}\\
\hspace{1em}Malaria season & 2.809 (P<0.001)\\
\hspace{1em}IRS status=After & 1.835 (P<0.001)\\
\hspace{1em}Rainy day & 3.765 (P<0.001)\\
\hspace{1em}Herd protection & -0.003 (P=0.368)\\
\hspace{1em}Malaria season:IRS status=After & -5.106 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Permanent not field worker}}\\
\hspace{1em}Malaria season & 0.831 (P<0.001)\\
\hspace{1em}IRS status=After & 1.151 (P<0.001)\\
\hspace{1em}Rainy day & 3.835 (P<0.001)\\
\hspace{1em}Herd protection & 0 (P=0.927)\\
\hspace{1em}Malaria season:IRS status=After & -1.66 (P<0.001)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary field worker}}\\
\hspace{1em}Malaria season & -0.188 (P=0.001)\\
\hspace{1em}IRS status=After & -0.254 (P<0.001)\\
\hspace{1em}Rainy day & 0 (P=0.994)\\
\hspace{1em}Herd protection & -0.001 (P=0.006)\\
\hspace{1em}Malaria season:IRS status=After & 0.054 (P=0.568)\\
\addlinespace[1.5em]
\multicolumn{2}{l}{\textbf{Temporary not field worker}}\\
\hspace{1em}Malaria season & 5.772 (P<0.001)\\
\hspace{1em}IRS status=After & -2.187 (P=0.023)\\
\hspace{1em}Rainy day & -1.349 (P=0.003)\\
\hspace{1em}Herd protection & 0.043 (P<0.001)\\
\hspace{1em}Malaria season:IRS status=After & -3.235 (P=0.003)\\*
\end{longtable}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-32-1.pdf}
\caption{i. Absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{figures/unnamed-chunk-33-1.pdf}
\caption{i. Sick absenteeism before and after IRS administration for all
workers who ever received IRS; ii. The same, but segregated by malaria
and non-malaria seasons}
\end{figure}

@@

\hypertarget{ref-Alaii2003FactorsAU}{}
Alaii, J.A., Hawley, W.A., Kolczak, M.S., Kuile, F.O.T., Gimnig, J.E.,
Vulule, J., Odhacha, A., Oloo, A.J., Nahlen, B.L., Phillips-Howard,
P.A., 2003. Factors affecting use of permethrin-treated bed nets during
a randomized controlled trial in western kenya. The American journal of
tropical medicine and hygiene 68 4 Suppl, 137--41.

@@

\hypertarget{ref-Binka2007}{}
Binka, F.N., Kubaje, A., Adjuik, M., Williams, L.A., Lengeler, C.,
Maude, G.H., Armah, G.E., Kajihara, B., Adiamah, J.H., Smith, P.G.,
2007. Impact of permethrin impregnated bednets on child mortality in
kassena-nankana district, ghana: A randomized controlled trial. Tropical
Medicine \& International Health 1, 147--154.
\url{https://doi.org/10.1111/j.1365-3156.1996.tb00020.x}

@@

\hypertarget{ref-Cohen2010}{}
Cohen, J., Dupas, P., 2010. Free distribution or cost-sharing? Evidence
from a randomized malaria prevention experiment. Quarterly Journal of
Economics 125, 1--45. \url{https://doi.org/10.1162/qjec.2010.125.1.1}

@@
